Definition list

### 2020-01-23 definitions.Rmd
update definitinos

---
title: "Definition list"
author: "Gerbrich Ferdinands"
date: "1/20/2020"
output: pdf_document
---
Term 1

~   Definition 1a
~   definition 1b
~ definition

Term 2 with *inline markup*

:   Definition 2

@@

>>>>

---
title: "Definition list"
author: "Gerbrich Ferdinands"
date: "1/20/2020"
output: pdf_document
---

Model.

:   The prediction model for Active learning

@@

Query Strategy
:   def

        add paragraph here

    Uncertainty sampling.
    :  Selects the least sure instances for labelling.

    Maximum sampling.
    :  Selects the samples with the highest prediction probability.

    Random and maximum sampling. 
    :  Combination of random and maximum sampling. By default samples the 95% of the instances with max sampling, and 5% of the samples with random sampling.

Feature Extraction Strategy
:   Feature Extraction Strategy

        { some code, part of Definition x }

    Third paragraph of definition x.

    Doc2Vec
    :

    Term frequency-inverse document frequency (tf-idf)
    :

    sbert
